О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-18 pps-linear-bound/pps-linear-lower-bound.tex
intersection of ... and ... -> intersection of ... with ...

Now we need to estimate the quanity of points in an intersection of an integral point set and a line segment.
There is the following estimate for minimum diameter of planar integral point sets with many collinear points:
\begin{theorem}~\cite[Theorem 4]{kurz2008minimum}
	For $\delta > 0$, $\varepsilon > 0$, and $P\in\mathfrak{M}(2,n)$ with
	at least $n^\delta$ collinear points there exists a $n_0 (\varepsilon)$
	such that for all $n \geq n_0 (\varepsilon)$ we have
	\begin{equation}
		\operatorname{diam} P \geq n^{\frac{\delta}{4 \log 2(1+\varepsilon)}\log \log n}
		.
	\end{equation}
\end{theorem}
However, the estimate is rather unsuitable for our needs,
as it does not provide the values of all the constants.
To obtain the desired estimate, we will now prove a generalization of~\cite[lemma 3]{our-vmmsh-2018}.

@@

	c) $N$ belongs to the intersection of one of $|M_1 M_2| - 1$ hyperbolas and $cr(M_3 M_4)$~---
	totally at most $4 (|M_1 M_2| - 1)$ points;

	d) $N$ belongs to the intersection of one of $|M_3 M_4| - 1$ hyperbolas and $cr(M_1 M_2)$~---
	totally at most $4 (|M_3 M_4| - 1)$ points;

@@

	\item
		intersection of ... and ...
		OR
		intersection of ... with ...
		?

>>>>

Now we need to estimate the quanity of points in an intersection of an integral point set with a line segment.
There is the following estimate for minimum diameter of planar integral point sets with many collinear points:
\begin{theorem}~\cite[Theorem 4]{kurz2008minimum}
	For $\delta > 0$, $\varepsilon > 0$, and $P\in\mathfrak{M}(2,n)$ with
	at least $n^\delta$ collinear points there exists a $n_0 (\varepsilon)$
	such that for all $n \geq n_0 (\varepsilon)$ we have
	\begin{equation}
		\operatorname{diam} P \geq n^{\frac{\delta}{4 \log 2(1+\varepsilon)}\log \log n}
		.
	\end{equation}
\end{theorem}
However, the estimate is rather unsuitable for our needs,
as it does not provide the values of all the constants.
To obtain the desired estimate, we will now prove a generalization of~\cite[lemma 3]{our-vmmsh-2018}.

@@

	c) $N$ belongs to the intersection of one of $|M_1 M_2| - 1$ hyperbolas with $cr(M_3 M_4)$~---
	totally at most $4 (|M_1 M_2| - 1)$ points;

	d) $N$ belongs to the intersection of one of $|M_3 M_4| - 1$ hyperbolas with $cr(M_1 M_2)$~---
	totally at most $4 (|M_3 M_4| - 1)$ points;

@@
